---
title: "Sample training polygons"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir=normalizePath("../.."))
```

Load libraries and scrips
```{r}
library(sf)
library(tidyverse)
source("code/lib/spatial-utils.R")
```

# Sample polygons used to extract pixels for training

Using labelme, polygons were drawn over ~50 ground-based photographs of regions within a coastal dune system (SHNA) consisting of a variety of ground cover classes (ex sand, vegetation)

These polygons were manually labeled so a training, validation, and testing set could be generated to classify pixels
at a pixel level using supervised machine learning.


# Define function to sample polygons

Because the quadrats were physically labeled in roman numerals 34-83, the ground-based images were placed into
directories  accordingly named. These folders are sometimes refereed to as "directories". Due to this naming scheme one should be careful as there are 50 directories,
1-50, but the quadrats are labeled 34-83.

The function sample_polygons takes in the json path and the directory (1-50) and gets the json created from label me.

```{r}
sample_polygons <- function(json) {
  json %>%
    label_me_json_to_sf() %>% # Helper defined in library (code/lib/veggie_utils.R)
    dplyr::mutate(area = st_area(.$polys)) %>%
    dplyr::mutate(label = case_when(label == "live Marram grass" ~ "live vegetation", TRUE ~ label)) %>%
    filter(is.element(label, c(
      "live vegetation", "dead vegetation", "sand"
    ))) %>%
    mutate(poly_num = c(1:length(polys)))
}
```

# Sample polygons and save for later use

```{r}
label_me_json_paths <-
  tibble(
    label_me_json_path = sprintf("clean_data/quadrats_old/quadrat%02d/rgb.json", seq(34, 83, 1)),
    directory = seq(1, 50)
  )

polys_sf <- label_me_json_paths %>%
  rowwise %>%
  mutate(polygons = list(sample_polygons(label_me_json_path))) %>%
  ungroup %>%
  unnest(cols = c(polygons))
  
#Save file in clean_data directory for future usage
#saveRDS(polys_sf, file = "clean_data/polygons/polys_sf.rds")
```

