---
title: "Vegetation Indicies"
author: "Jackson Krebsbach"
date: "10/17/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(raster)
library(ggplot2)
library(latex2exp)
library(ggeasy)
```



```{r include=FALSE}

## Vegetation Index Functions
Multi.Vegetation.Index<- function(subIm){(subIm[[5]]-subIm[[3]])/(subIm[[5]]+subIm[[3]])}
Multi.Renormalized <- function(subIm){(subIm[[5]]-subIm[[3]])/(sqrt(subIm[[5]]+subIm[[3]]))}
Multi.Simple.Index<- function(subIm){(subIm[[5]])/(subIm[[3]])}
Multi.VARI <- function(subIm){(subIm[[2]]-subIm[[3]])/(subIm[[2]]+subIm[[3]]-subIm[[1]])}
Multi.TGI <- function(subIm){(190*(subIM))/2}
Multi.NLI<- function(subIm){((subIm[[5]])^2-subIm[[3]])/((subIm[[5]])^2+subIm[[3]])}
Multi.TGI<- function(subIm){((193*(subIm[[3]]-subIm[[2]]))-(108*(subIm[[3]]-subIm[[1]])))/2}
Multi.NDRE <- function(subIm){(subIm[[4]]-subIm[[3]])/(subIm[[4]]+subIm[[3]])}
Multi.SAVI <- function(subIm){((subIm[[5]]-subIm[[3]])/(subIm[[5]]+subIm[[3]]+1))*2}

load("./RData/ground_dat_200.RData")
load("./RData/drone_dat_200.RData")
```

## Live_Veg vs. Ave NDVI

Comparison Using the Normalized Difference Vegetation Index

$$\textrm{NDVI}=\frac{\textrm{NIR}-\textrm{RED}}{\textrm{NIR}+\textrm{RED}}$$

Multiple R-squared:  0.8338

```{r}
ground_dat <- ground_dat_200
drone_dat <- drone_dat_200
ndvi <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)
fit<- lm(live_veg ~ poly(ndvi,degree=2))
prd <- data.frame(hp = seq(from = range(ndvi)[1], to = range(ndvi)[2], length.out = 200))
err <- predict(fit, newdata = prd, se.fit = TRUE)

prd$lci <- err$fit - 1.96 * err$se.fit
prd$fit <- err$fit
prd$uci <- err$fit + 1.96 * err$se.fit

#theme_update(plot.title = element_text(hjust = 'center'))
ggplot(prd, aes(x = ndvi, y = fit))+ ggtitle("Live Vegetation vs. NDVI") +
  theme_bw() +
  geom_line() +
 # geom_smooth(aes(ymin = lci, ymax = uci), stat = "identity") +
  geom_point(aes(x = ndvi, y = live_veg)) + xlab('NDVI') + ylab('Live Vegetation')+
  theme(plot.title = element_text(hjust = 0.5))
```






```{r echo=FALSE,fig.align="center"}

ground_dat <- ground_dat_200
drone_dat <- drone_dat_200

ndvi <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)

regression<- lm(live_veg ~ poly(ndvi,degree=2))
dev.new(width=5, height=5, unit="in")
plot(ndvi,live_veg, xlab = "Average NDVI", ylab = "Coverage", cex = 0.75, cex.lab = 1.25, pch= 1)


#summary(regression)

r_squared = format(summary(regression)$adj.r.squared, digits=3)


new<- data.frame(ndvi = sort(ndvi))
pre <- predict(regression,newdata = new)

lines(new$ndvi,pre, col = "blue")
legend("topleft", bty="n", legend = TeX("$R^2= 0.832$"), x.intersp=0, xjust=0, yjust=0, cex = 1.25 )
```

## Live Veg vs VARI

Visibily Atmospherically Resistant Index
$$\textrm{VARI}=\frac{\textrm{GREEN}-\textrm{RED}}{\textrm{GREEN}+\textrm{RED}-\textrm{1}}$$

Multiple R-squared:  0.8338
```{r echo=FALSE,fig.align="center"}
load("./RData/drone_dat_VARI_200.RData")


ground_dat <- ground_dat_200
drone_dat <- drone_dat_VARI_200

vari <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)

regression<- lm(live_veg ~ poly(vari,degree=2))
plot(vari,live_veg)
#summary(regression)

new<- seq(min(vari),max(vari),0.01)
new
pre <- predict(regression,newdata = new,inverval = "prediction")
lines(new,pre, col = "blue")


```


## Live Veg vs Simple

Simple/Ratio Vegetation Index
$$\textrm{SIMPLE}=\frac{\textrm{NIR}}{\textrm{RED}}$$
Multiple R-squared:  0.8156
```{r echo=FALSE,fig.align="center"}
load("./RData/drone_dat_simple_200.RData")

ground_dat <- ground_dat_200
drone_dat <- drone_dat_Simple_200

simple <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)

regression<- lm(live_veg ~ poly(simple,degree=2))
plot(simple,live_veg)
#summary(regression)

new<- data.frame(simple = sort(simple))
pre <- predict(regression,newdata = new,inverval = "prediction")
lines(new$simple,pre, col = "blue")
```


## Live Veg vs RDVI

Renormalized Difference Vegetation Index

$$\textrm{RDVI}=\frac{\textrm{NIR}-\textrm{RED}}{\sqrt{\textrm{NIR}+\textrm{RED}}}$$

Multiple R-squared:  0.8506
```{r echo=FALSE,fig.align="center"}

load("./RData/drone_dat_RDVI_200.RData")

ground_dat <- ground_dat_200
drone_dat <- drone_dat_RDVI_200

rdvi <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)

regression<- lm(live_veg ~ poly(rdvi,degree=2))
plot(rdvi,live_veg)
#summary(regression)

new<- data.frame(rdvi = sort(rdvi))
pre <- predict(regression,newdata = new,inverval = "prediction")
lines(new$rdvi,pre, col = "blue")
```

## Live Veg vs. TGI

Triangular Vegetation Index

Multiple R-squared:  0.03284
```{r echo=FALSE,fig.align="center"}

load("./RData/drone_dat_TGI_200.RData")

ground_dat <- ground_dat_200
drone_dat <- drone_dat_TGI_200

tgi <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)

regression<- lm(live_veg ~ poly(tgi,degree=2))
plot(tgi,live_veg)
#summary(regression)

new<- data.frame(TGI = tgi)
pre <- predict(regression,newdata = new,inverval = "prediction")
lines(sort(tgi),sort(pre), col = "blue")


```

## Live Veg vs. NLI

Non-Linear Index
$$\textrm{NLI}=\frac{{\textrm{NIR}}^2-\textrm{RED}}{{\textrm{NIR}}^2+\textrm{RED}}$$
Multiple R-squared:  0.4931
```{r echo=FALSE,fig.align="center"}
load("./RData/drone_dat_NLI_200.RData")


ground_dat <- ground_dat_200
drone_dat <- drone_dat_NLI_200

nli <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)

regression<- lm(live_veg ~ poly(nli,degree=2))
plot(nli,live_veg)
#summary(regression)

new<- data.frame(NLI = nli)
pre <- predict(regression,newdata = new,inverval = "prediction")
lines(sort(nli),sort(pre), col = "blue")
```

## Live Veg vs. NDRE

Normalized Difference Red Index
$$\textrm{NDRE}=\frac{\textrm{NIR} -\textrm{RED_EDGE}}{\textrm{NIR}+\textrm{RED_EDGE}}$$



Multiple R-squared:  0.7841
```{r echo=FALSE,fig.align="center"}
load("./RData/drone_dat_NDRE_200.RData")

ground_dat <- ground_dat_200
drone_dat <- drone_dat_NDRE_200

ndre <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)

regression<- lm(live_veg ~ poly(ndre,degree=2))
plot(ndre,live_veg)
#summary(regression)

new<- data.frame(NDRE = ndre)
pre <- predict(regression,newdata = new,inverval = "prediction")
lines(sort(ndre),sort(pre), col = "blue")

```

## Live Veg vs. SAVI

Soil-adjusted vegeation index
$$\textrm{NDVI}=2\times\frac{\textrm{NIR}-\textrm{RED}}{\textrm{NIR}+\textrm{RED}+1}$$
Multiple R-squared:  0.8338
```{r echo=FALSE,fig.align="center"}

load("./RData/drone_dat_SAVI_200.RData")

ground_dat <- ground_dat_200
drone_dat <- drone_dat_SAVI_200

savi <- as.numeric(drone_dat$Ave_NDVI)
live_veg <- as.numeric(ground_dat$`%live veg`)

regression<- lm(live_veg ~ poly(savi,degree=2))
plot(savi,live_veg)
#summary(regression)

new<- data.frame(SAVI = savi)
pre <- predict(regression,newdata = new,inverval = "prediction")
lines(sort(savi),sort(pre), col = "blue")



```

## Live Veg vs. PVI
```{r echo=FALSE}
drone_image <- brick("./Drone_Stitched/ortho.tif")

#NIR<- extract(drone_image[[5]],extent(drone_image[[5]]),method =`simple`)
#RED<- extract(drone_image[[3]], extent(drone_image[[3]]),method = `simple`)

NIR <- drone_image[[5]]
RED <- drone_image[[3]] 

plot(NIR,RED,xlim = c(0,25000), ylim = c(0,15000))


```

## Live Veg vs. Hand Counts

Live Vegeation estimates using classified ground imagery vs. HandCounts

Multiple R-squared:  0.4836
```{r echo=FALSE,fig.align="center"}
df <- read.csv("./Misc/Stem_Counts.csv")


live_veg <- as.numeric(ground_dat_200$`%live veg`)

stems <- as.data.frame((df[3:8]))
stems<- as.numeric(rowSums(stems))

regression<- lm(live_veg ~ poly(stems,degree=2))
#summary(regression)

new<- data.frame(stems = sort(stems))
pre <- predict(regression, newdata = new,inverval = "prediction")
plot(stems,live_veg)
lines(new$stems,pre, col = "blue")

#plot(as.numeric(df$mStems)+as.numeric(df$srStems)+as.numeric(df$mwStems),jitter(df$ggtCov,2) )
#plot(live_veg,jitter(df$ggtCov,2),xlim = c(0,0.5),ylim = c(0,15))
```

## Not Live vs Hand Counts
```{r echo=FALSE,fig.align="center"}
#df <- read.csv("/Volumes/GoogleDrive/My Drive/Research/Research_2019/Stem_Counts.csv")
#load("/Volumes/GoogleDrive/My Drive/Research/Research_2019/drone_dat_200.RData")
#load("/Volumes/GoogleDrive/My Drive/Research/Research_2019/ground_dat_200.RData")
handcounts_not_live <- as.numeric(1-df$ggtCov)
ground_not_live <- as.numeric(ground_dat_200$`%sand`)+as.numeric(ground_dat_200$`%dead veg`)

regression<- lm(handcounts_not_live ~ poly(ground_not_live,degree=2))
plot(ground_not_live,handcounts_not_live)
#summary(regression)

new<- data.frame(ground_not_live = sort(ground_not_live))
pre <- predict(regression, newdata = new,inverval = "prediction")

lines(new$ground_not_live,pre, col = "blue")
```
